\section{Conclusion and Future Work}
This paper has presented the design, implementation, and empirical evaluation of a lightweight Digital Rights Management (DRM) system optimized for high-throughput video distribution. By abandoning the traditional paradigm of full-stream cryptographic encapsulation, the proposed framework exploits the syntactic structures of the H.264/AVC codec to implement an intelligent, codec-aware Selective Encryption (SE) mechanism. 

The empirical evaluations demonstrate that encrypting only critical structural anchoring segments—specifically the Instantaneous Decoder Refresh (IDR) frames along with the Sequence and Picture Parameter Sets (SPS/PPS)—substantially mitigates client-side computational latency. The system achieved up to a 93.04\% reduction in decryption processing times for high-definition, large-scale video assets while drastically lowering client CPU utilization from a 14.5\% baseline down to a negligible 1.1\%. Furthermore, the data throughput rate climbed significantly, achieving a maximum processing multiplier of $14.38\times$ on high-bitrate streaming loads. Concurrently, simulated attack metrics verified that unauthorized playback attempts fail completely, yielding extreme visual degradation ($\text{PSNR} = 6.25\text{ dB}$ and $\text{SSIM} = 0.02$) that renders the intercepted content entirely unwatchable. Thus, the system successfully bridges the operational gap between robust data confidentiality and hardware efficiency.

Future work will focus on expanding this lightweight DRM architecture along three programmatic paths:
\begin{enumerate}
    \item \textbf{Advanced Codec Support:} Extending the codec parsing engine to accommodate modern compression standards, such as H.265/High Efficiency Video Coding (HEVC) and AV1, which rely on different NAL unit mapping geometries.
    \item \textbf{Dynamic Adaptive Streaming Integration:} Embedding the cryptographic selectively-encrypted payload structures directly into production streaming protocols like HTTP Dynamic Adaptive Streaming over HTTP (DASH) and HTTP Live Streaming (HLS).
    \item \textbf{Hardware Security Integration:} Migrating the client-side volatile memory key handling into dedicated Trusted Execution Environments (TEEs) or Android-based Widevine Level 1 equivalent secure storage to strengthen protection against local memory dumping vectors.
\end{enumerate}