\section{Proposed Lightweight DRM Architecture}
The core objective of the proposed architecture is to decouple the high-throughput video content delivery network (CDN) from the sensitive cryptographic key management layer. To achieve a lightweight operational footprint, the system architecture is partitioned into three distinct operational layers: the Media Content Packager, the Centralized License Server, and the DRM Client Player.

\subsection{Threat Model and Security Assumptions}
To evaluate the security architectural bounds of the proposed lightweight DRM system, we define a formal threat model based on an active adversary profile. The primary adversary is assumed to be an unauthorized client package interceptor or a rogue distribution endpoint with the following capabilities and constraints:
\begin{itemize}
    \item \textbf{Network Eavesdropping:} The adversary can intercept the encrypted transport stream directly from the Content Delivery Network (CDN) or intermediate network routing nodes.
    \item \textbf{Codec Compliant Decoding:} The adversary possesses a standard, fully compliant H.264/AVC multimedia decoder but lacks access to the platform API gateway and does not hold a valid cryptographic token or the 128-bit Content Encryption Key (CEK).
    \item \textbf{Exclusion of Side-Channels:} Physical tampering with the client hardware memory lines (such as runtime kernel dumping or cryptographic side-channel evaluation) is considered outside the scope of this baseline threat model.
\end{itemize}
The security goal is centered on perceptual confidentiality—ensuring that unauthorized decoding attempts render the multimedia content visually unwatchable and commercial extraction unviable, rather than full computational hiding of the entire stream.

\subsection{Syntax-Aware Selection Rationale (SPS/PPS/IDR)}
The strategic encapsulation of only specific Network Abstraction Layer (NAL) unit types, specifically types 5, 7, and 8 is governed by structural dependencies within the H.264/AVC Annex-B syntax specification.
\begin{itemize}
    \item \textbf{Sequence Parameter Sets (SPS, Type 7):} Contains global configuration parameters governing the entire video sequence, including decoding profile bounds, frame dimensions, and chroma sampling ratios.
    \item \textbf{Picture Parameter Sets (PPS, Type 8):} Defines localized variables applicable to successive picture segments, such as entropy coding mode selections (CABAC/CAVLC) and quantization constraints.
    \item \textbf{Instantaneous Decoder Refresh (IDR, Type 5):} Serves as the strict temporal and spatial boundary frame. Subsequent inter-frame macroblocks are mathematically prohibited from referencing frames prior to the IDR.
\end{itemize}
By targeting these three components, the encryption mutations strike the foundational structural data. Without compiling valid parameter parsing headers, standard decoders cannot initialize the local slice configuration contexts. Furthermore, because the baseline reference pixels within the IDR frames are hidden, dependent Predictive (P) and Bi-predictive (B) frames cannot resolve temporal motion vector displacements, neutralizing the bulk content without cryptographic interaction.

\subsection{The Media Content Packager Pipeline}
The Media Content Packager acts as an offline ingestion engine that transforms standard, unprotected H.264/AVC video files into cryptographically secured assets. Rather than applying a blanket encryption sweep across the entire binary file payload, the packager deploys a lightweight, codec-aware parsing mechanism.

The inner operational sequence of the packaging pipeline is structured as follows:
\begin{enumerate}
    \item \textbf{Bitstream Parsing:} The packager ingests the raw H.264 transport stream and scans the continuous byte sequence to identify the start codes (\texttt{0x000001} or \texttt{0x00000001}). It extracts the subsequent 1-byte NAL unit header to evaluate the \texttt{nal\_unit\_type} bits.
    \item \textbf{Structural Isolation:} NAL units with a \texttt{nal\_unit\_type} value of 5 (IDR frame), 7 (SPS), or 8 (PPS) are routed to the high-priority cryptographic queue. All other VCL units (P and B frame slices) bypass the cryptographic engine and are pushed directly to the output muxer in the clear.
    \item \textbf{Key and IV Generation:} For each video asset, a 128-bit Content Encryption Key (CEK) and a 64-bit base Initialization Vector (IV) are generated using a cryptographically secure pseudo-random number generator (CSPRNG).
    \item \textbf{Selective Encryption Processing:} The high-priority NAL unit payloads are encrypted via the AES-CTR engine utilizing the generated CEK and IV.
    \item \textbf{Encapsulation and Metadata Injection:} The packager re-interleaves the newly encrypted structural NAL units with the unencrypted P/B units. To ensure the client player can correctly identify and initialize the decryption loop, a custom, unencrypted DRM Metadata Header is injected at the front of the output file container. This header encapsulates the globally unique asset identifier (\texttt{Content\_ID}) and the explicit $\text{IV}$ parameters.
\end{enumerate}

\subsection{Token-Based License Server Architecture}
To prevent key exposure, Content Encryption Keys are never stored within the distributed media files or content delivery networks. Instead, the packager transmits a secure mapping tuple comprising $(\text{Content\_ID}, \text{CEK})$ to the Centralized License Server via a TLS 1.3 protected endpoint. The License Server manages key lookup, access control verification, and dynamic license dispatch.

The license acquisition flow incorporates a token-based authentication mechanism using JSON Web Tokens (JWT). When a client requests access to a specific video stream, the sequence unfolds as follows:
\begin{enumerate}
    \item The client authenticates against the primary platform API Gateway using its user credentials.
    \item Upon successful validation, the gateway issues a time-bound, ephemeral JWT signed with the server's private key using the RS256 algorithm. The token payload explicitly binds the user's identity, an expiration timestamp, and the authorized \texttt{Content\_ID}.
    \item The client presents this signed JWT directly to the License Server's request endpoint.
    \item The License Server verifies the cryptographic signature of the token using the gateway's public key, checks for token expiration, and extracts the embedded \texttt{Content\_ID}.
    \item Upon successful validation, the server retrieves the corresponding 128-bit CEK from its key database, wraps it in a secure JSON license response payload, and dispatches it back to the client player.
\end{enumerate}

\subsection{Client-Side Lightweight Decryption Loop}
The DRM Client Player is engineered to perform real-time, low-overhead decryption directly within the media rendering pipeline. By isolating the cryptographic processing strictly to the required structural units, the client avoids filling CPU cache lines or consuming GPU acceleration cycles with unnecessary full-stream decipher operations.

Upon loading the media asset, the player's custom demuxer reads the DRM Metadata Header to extract the \texttt{Content\_ID} and the base $\text{IV}$. The player then initiates an asynchronous handshake with the Centralized License Server, passing the signed JWT to acquire the 128-bit CEK. Once the CEK is securely loaded into the volatile memory space of the local cryptographic context, the real-time playback loop commences.

As chunks of the H.264 stream are fed into the input buffer, the demuxer inspects the NAL unit headers in real-time. If a standard, unencrypted VCL unit (P or B frame) is detected, the packet bypasses the cryptographic subsystem completely and is piped directly to the hardware video decoder. Conversely, when an encrypted NAL unit (\texttt{nal\_unit\_type} $= 5, 7, \text{ or } 8$) is encountered, the player invokes a lightweight AES-CTR execution thread. The thread applies the XOR keystream to restore the plaintext NAL payload and seamlessly hands the reconstructed segment to the hardware decoder interface. This design ensures that the high-volume data path remains unencumbered by cryptographic latency.